Mahotas: Open source software for scriptable computer vision

### 2012-08-24 paper.tex
TXT Mahotas works for Python 3 now
BIB Reference distance map algorithm
I think this is one of the few that is young enough to not be just part
of the culture (along with SURF, of course).

Mahotas is a computer vision library for the Python. It operates on numpy
arrays~\citep{numpystructure}. Therefore, it uses all the infrastructure built
by that project for storing information. In particular, unlike libraries
written in the C~Language or in Java~\citep{Marcel:2010:TMP:1873951.1874254},
Mahotas does not need to define a data structure, but uses the numpy array
structure. Many basic manipulation functionality that would otherwise be part
of a computer vision library are handled by numpy, for example computing
averages and other simple statistics, handling multi-channel images, converting
between types (integer and floating point images are supported by mahotas,
whenever it is meaningful). For the user, this has the additional advantage
that they do not need to learn yet another set of functions.

@@

\begin{description}
\item[\textsc{surf}] Speeded-up Robust Features~\citep{eth_biwi_00517}. This is
a collection of local features.
\item[features] Global feature descriptors. In particular, Haralick texture
features, Zernike moments, local binary patterns, threshold adjacency
statistics.
\item[Wavelet] Haar and Daubechies wavelets. Forward and reverse transforms.
\item[morphological functions] Erosion and dilation, as well as some more
complex operations built on these. There are both binary and grayscale
implementations of these operators.
\item[watershed] seeded watershed and distance map transforms.
\item[filtering] Gaussian filtering and general convolutions.
\item[polygon operations] convex hull, polygon drawing.
\end{description}

>>>>

Mahotas is a computer vision library for the Python Programming Language
(versions 2.5 and up, including version 3). It operates on numpy
arrays~\citep{numpystructure}. Therefore, it uses all the infrastructure built
by that project for storing information. In particular, unlike libraries
written in the C~Language or in Java~\citep{Marcel:2010:TMP:1873951.1874254},
Mahotas does not need to define a data structure, but uses the numpy array
structure. Many basic manipulation functionality that would otherwise be part
of a computer vision library are handled by numpy, for example computing
averages and other simple statistics, handling multi-channel images, converting
between types (integer and floating point images are supported by mahotas,
whenever it is meaningful). For the user, this has the additional advantage
that they do not need to learn yet another set of functions.

@@

\begin{description}
\item[\textsc{surf}] Speeded-up Robust Features~\citep{eth_biwi_00517}. This is
a collection of local features.
\item[features] Global feature descriptors. In particular, Haralick texture
features, Zernike moments, local binary patterns, threshold adjacency
statistics.
\item[Wavelet] Haar and Daubechies wavelets. Forward and reverse transforms.
\item[morphological functions] Erosion and dilation, as well as some more
complex operations built on these. There are both binary and grayscale
implementations of these operators.
\item[watershed] seeded watershed and distance map
transforms~\citep{felzenszwalb}.
\item[filtering] Gaussian filtering and general convolutions.
\item[polygon operations] convex hull, polygon drawing.
\end{description}
